% ============================================================
% Paragraphs: Real-Market SPY Calibration Results (100-contract version)
% For use in the Experiments section of the thesis/paper
% ============================================================

%--- Market Data and Pre-processing ---%
To evaluate the proposed calibration framework under realistic market conditions, we employ SPY (SPDR S\&P~500 ETF Trust) call option data from two consecutive trading days: 2022-09-01, used for calibration, and 2022-09-02, used for out-of-sample validation. The descriptive statistics of the two option chains are summarised in Table~\ref{tab:spy_data}. On both days, the underlying spot price lies near \$392--396 and the retained contracts span roughly 77--106 calendar days to expiry, so the sample is still fairly concentrated in maturity even though it now contains 100 contracts per day rather than a tiny near-the-money subset. Mid-quote prices (average of bid and ask) are adopted as market prices. Implied volatilities and Vega values are subsequently recovered via Black--Scholes inversion using \texttt{py\_vollib\_vectorized}, and contracts for which the inversion fails (below-intrinsic or zero-Vega quotes) are discarded before the final centred block of 100 contracts is selected.

The risk-free rate is obtained from the Federal Reserve's daily par yield curve spanning 2020--2023. Par yields at the standard maturity nodes (1, 2, 3, 6, and 12 months) are first converted to continuously compounded rates via $r_c = \ln(1 + R_{\text{par}} \cdot t)\,/\,t$, and the term structure is then interpolated at the exact option maturity using a cubic spline. This procedure yields maturity-matched continuous rates in the range 2.894\%--3.027\% on 2022-09-01 and 2.870\%--2.986\% on 2022-09-02. Options are further filtered to retain only those with positive trading volume, days-to-expiry between 40 and 300, and log-moneyness $\ln(K/S_0) \in [-0.15,\, 0.20]$. After cleaning, 100 call contracts are retained from the centre of each filtered chain for calibration and validation.

%--- Same-Day Calibration ---%
Table~\ref{tab:spy_sameday} reports the same-day calibration performance, where each method is calibrated on and evaluated against the 2022-09-02 option chain. On this 100-contract SPY sample, the proposed method achieves an implied-volatility Mean Relative Error (IV MRE) of \textbf{1.56\%}, compared with \textbf{5.01\%} for Zhang~(2025), when the baseline's price outputs are converted back to Black--Scholes implied volatilities. This is a much clearer separation than in the earlier 10-contract toy comparison and suggests that the IV-space objective keeps the fitted surface closer to the market IV surface once the sample contains a broader strike range. Zhang~(2025) still has an advantage in its native price metric, with a same-day price MRE of 13.36\%, which is expected because the baseline is optimised directly in normalised price space. Under QuantLib re-pricing, the proposed method attains an IV MRE of 8.15\% versus 9.18\% for Zhang~(2025), while the corresponding price MREs are 18.10\% and 16.93\%, respectively.

%--- Cross-Day Calibration ---%
Table~\ref{tab:spy_crossday} reports the cross-day calibration experiment, in which the Heston parameters calibrated on the 2022-09-01 chain are applied without re-calibration to predict the 2022-09-02 option prices and implied volatilities. This scenario directly measures the temporal stability of the calibrated parameters under a one-day horizon. The proposed method achieves a cross-day IV MRE of \textbf{1.98\%}, compared with \textbf{3.71\%} for Zhang~(2025), so it still delivers the lower next-day IV error on the evaluation chain. In addition, its QuantLib re-pricing errors remain smaller: the cross-day QuantLib IV MRE is 9.23\% versus 10.79\%, and the cross-day QuantLib price MRE is 18.89\% versus 20.70\%. Relative to the same-day baseline, the proposed method's native IV MRE increases by only 0.42 percentage points. The Zhang baseline shows a negative change in the derived IV metric (from 5.01\% to 3.71\%), but this should not be over-interpreted as superior temporal robustness, because the model is not calibrated in IV space and the reported IV MRE is obtained only after an additional Black--Scholes inversion of price predictions. Overall, the results indicate that the proposed IV-space calibration framework, augmented by Feller regularisation, produces more reliable IV-surface fitting on the next trading day while remaining competitive in structural Heston re-pricing.
